---
title: 'Manuscript'
output:  
  bookdown::pdf_document2:
    fontsize: 12pt
    fontfamily: helvetica
    keep_tex: yes #keep LaTeX file for submission
    fig_caption: yes #allows captions in figures
    toc: false #do not include table of contents
    extra_dependencies:
      subfig: null #allows for subfigures
      breqn: null #line breaks for long equations
      caption: ["font={small}"] #size of the figure captions
    includes:
      in_header: latex_docs/preamble.sty #additional LaTeX formatting
  bookdown::word_document2:
    fig_caption: yes #figure caption
    reference_docx: "docx_template.docx"
    keep_md: yes
  bookdown::html_document2:
    css: "html_docs/style.css" #style for the HTML document
csl: bibliography/american-medical-association.csl #style for references
bibliography: bibliography/refs.bib #references
link-citations: yes #adds links to the citations
urlcolor: blue
'': default
---

# Abstract

Suspendisse aliquam lectus nunc, sed accumsan felis convallis non. Praesent in ex eu lacus cursus cursus aliquam vitae massa. Phasellus nibh tellus, suscipit at efficitur eget, varius nec lacus. Maecenas consequat fringilla ligula, in tempus ipsum dictum quis. Proin ac est blandit velit dignissim ultricies. Quisque bibendum eu nulla eu euismod. Praesent aliquam convallis metus a tincidunt.


# Keywords {-}

science; living systems; research

```{r libraries, message = FALSE,include=FALSE}
#the packages needed to run the code

library(patchwork)
library(tidyverse)
library(here)
library(showtext)
library(jpeg)
library(ggpmisc)
library(grid)
library(png)
library(scico)
set.seed(2021) #set seed for reproducibility

thm1<-scale_fill_scico_d(palette="imola",begin=0, end=1, direction = 1, aesthetics = c("colour","fill"))

#font_add("Atkinson",regular="AtkinsonHyperlegible-Regular.ttf",italic="AtkinsonHyperlegible-Italic.ttf")
showtext_auto()

#this function will remove the default "author information" that is the Pandoc LaTeX template. Otherwise, and additional "and" will appear at the end of the author list.Or, the custom template that is in the YAML header and that has the "author" line deleted may be used as well. An explanation in detail is provided at:
#https://github.com/rstudio/bookdown/issues/1158
remove_author <- function(x) {
  # identify empty author line
  i <- grep("^\\\\author\\{\\}$", x)
  # be sure it is the one pandoc inserts
  if(length(i) != 0 && grepl('^\\\\date\\{', x[i+1])) x <- x[-i]
  x
}
options(bookdown.post.latex = remove_author)
```


```{r child='sections/01-Introduction.Rmd'}
```



```{r child='sections/02-Materials-and-Methods.Rmd'}
```



```{r child='sections/03-Results.Rmd'}
```



```{r child='sections/04-Discussion.Rmd'}
```



```{r child='sections/05-Conclusion.Rmd'}
```


***
# References

<div id="refs"></div>
